\Huge\textbf{Mbrane}\linebreak\linebreak\linebreak \Large\textbf{Final Report}\linebreak\linebreak \linebreak\linebreak \includegraphics[scale=0.1]{feup-logo.png}\linebreak\linebreak \linebreak\linebreak \Large{Logic Programing}\linebreak

### 2019-11-18 docs/report_latex/template.tex
Final version

% TODO complete
\subsection{Plays of the computer} 
The computer plays only in an easy difficulty setting, this means that for each turn of the computer we get all the possible plays using 
the \textit{valid\_moves(+Board, -R)} predicate. Then using the \textit{random/3} predicate from the SicStus random library we chose a random 
move and execute it. The predicate that makes the move move of the computer is \textit{bot\_turn(+Board,+Power,-Result)}.

@@

\paragraph{}
We had a lot of trouble during the development of the project. Everything started on our first
approach to internally store and use the game board. Only when we were trying to make 
the game "playable" did we realize our approach was not the best one, as we were not finding a 
way to make the game play past the second round. This required an almost total refactoring of
the code which made us loose a lot of time. We ended up not having time to implement a more 
difficult game mode agains the computer using a little aritifitial inteligence wich was 
something we were looking forward to do. Due to these time issues we also ended up not implementing
the final \textit{Resolution Phase}. We made this decision having in mind it whould not add much complexity
to the project as it is only a bunch of calculations.

>>>>

% TODO complete
\subsection{Plays of the computer} 
The computer plays only in an easy difficulty setting, this means that for each turn of the computer we get all the possible plays using 
the \textit{valid\_moves(+Board, -R)} predicate. Then using the \textit{random/3} predicate from the SicStus random library, we choose a random 
move and execute it. The predicate that makes the move move of the computer is \textit{bot\_turn(+Board,+Power,-Result)}.

@@

\paragraph{}
We had a lot of trouble during the development of the project. Everything started on our first
approach to internally store and use the game board. Only when we were trying to make 
the game "playable" did we realize our approach was not the best one, as we were not finding a 
way to make the game play past the second round. This required an almost total refactoring of
the code which made us loose a lot of time. We ended up not having time to implement a more 
difficult game mode agains the computer using a little aritifitial inteligence which was 
something we were looking forward to do. Due to these time issues we also ended up not implementing
the final \textit{Resolution Phase}. We made this decision having in mind it whould not add much
 complexity to the project as it would only involve some calculations using already existing preicates.
